Replication and Extension of Analyses Regarding Effects of Highly Restrictive Abortion Policies

### 2021-12-16 paper_replication.Rmd
Update paper_replication.Rmd

We did observe a decrease in abortion rates based on estimated distances to abortion providers.  This decrease was statistically significant, but not practically significant at -3.4 x 10^-6 abortions per 1,000 women (see Table 4), compared to -0.02 in the analysis by Brown et al.

>>>>

We did observe a decrease in abortion rates based on estimated distances to abortion providers.  This decrease was statistically significant significant at -0.00554 abortions per 1,000 women (see Table 4), compared to -0.02 in the analysis by Brown et al.
